High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 Experiments.tex
fixing and clarifying description of experiments with NGE

Tasks do not wait within the Agent's queue since one node is available to
each AthenaMP instance. Task execution  overheads result primarily from
three factors: (i) the initial bootstrapping of the pilot on the nodes; (ii)
the UnitManager's dispatching of units (tasks) to the agent; and (iii) time
for the agent to bootstrap all the tasks on the nodes.

@@

We ran pilots with 256, 512, 1024 and 2048 worker nodes and 3\mtnote{2?}
hours walltime. Fig.~\ref{fig:weakScal2a} depicts the average pilot duration,
the average execution time of five sequential generations of AthenaMP, and
the corresponding overhead. The difference between the two durations is more
marked than in the previous experiments. Despite this, we notice that the
growth of the overhead is consistent with the increment of the number of
tasks per node for pilots with 256, 512 and 1024 worker nodes, and less than
linear for the pilot with 2048 worker nodes.

@@

We investigate strong scalability by running the same number of tasks for
different pilot sizes. We used 2048 AthenaMP instances and pilots with 256,
512, 1024 and 2048 nodes. Thus, the number of AthenaMP generations is equal
to eight times the size of the smallest pilot and corresponds to the size of
the largest pilot. As a consequence, the number of consecutive generations of
AthenaMP decreases with the pilot size. These experiments are designed to
investigate whether pilot overhead is affected by the degree of concurrency
within the pilot and/or the number of tasks. Each AthenaMP instance simulates
sixteen events as in the previous experiment.

>>>>

Tasks do not wait within the Agent's queue since one node is available to
each AthenaMP instance. Task execution  overheads result primarily from
three factors: (i) the initial bootstrapping of the pilot on the nodes; (ii)
the UnitManager's dispatching of units (tasks) to the agent; and (iii) time
for the Agent to bootstrap all the tasks on the nodes.

@@

We ran pilots with 256, 512, 1024 and 2048 worker nodes and 3 hours walltime.
Fig.~\ref{fig:weakScal2a} depicts the average pilot duration, the average
execution time of five generations of AthenaMP, and the
corresponding overhead. The difference between the two durations is more
marked than in the previous experiments. Despite this, we notice that the
growth of the overhead is consistent with the increment of the number of tasks
per node for pilots with 256, 512 and 1024 worker nodes, and less than linear
for the pilot with 2048 worker nodes.

@@

We investigate strong scalability by running the same number of tasks for
different pilot sizes. We used 2048 AthenaMP instances and pilots with 256,
512, 1024 and 2048 nodes. Thus, the number of AthenaMP instances per node
(i.e., generations) is eight for the smallest pilot (256 nodes), one for the
largest pilot (2048 nodes), and with the number of generations of AthenaMP
decreasing with the pilot size. These experiments are designed to investigate
whether pilot overhead is affected by the degree of concurrency within the
pilot and/or the number of tasks. Each AthenaMP instance simulates sixteen
events as in the previous experiment.
